---
title: "Functions.Rmd"
author: "issa fall"
date: "June 30, 2015"
output: html_document.


## Question1
```
Captain Jack is convinced that he can predict how much gold he will find on
an island with the following equation: (a*b)-c*324+log(a),where a is the area
of the island in square meters,b is the number of trees on the island, and c
is how drunk he is on a scale of 1 to 10.Create a function called Jacks.Equation
that takes a,b, and c as arguments and returns Captain Jack's predictions.Test
your function for an island with an area of 1000 square meters that contains 30
trees when Jack is at a 7/10 on a drunkenness scale
```
```{r,echo=TRUE}
Jacks.Equation<-function(a,b,c){
  output<-(a*b)-c*324+log(a)
  return(output)
}
Jacks.Equation(a=1100,b=100,c=4)
```
## Question2
Write a function called Standardize.me that takes vector x as an argument,
and returns a vector that standardizes the values of x (standardization means
substracting the mean and dividing by the standard deviation)
```{r,echo=TRUE}
Standardize.me<-function(x){
  output<-(x-mean(x)/sd(x))
  return(output)
}
data<-c(3,4,19,7,5,5,10,200)
Standardize.me(data)
```
## Question3
Write a function called remove.Outliers that takes a vector as an argument,
determines which values of the vector are outliers,and returns a vector
with the outliers removed.Define an outlier as any value that is less than 
2 standard deviations below the mean,or more than 2 standard deviations above
the mean.
```{r,echo=TRUE}
remove.Outliers<-function(x){
  is.outlier<-x > mean(x)+2*sd(x) | x < mean(x)-2*sd(x)
  new.vector<-x[(is.outlier == FALSE)]
  return(new.vector)
}
```
##Generating random numbers from a linear model
```{r,echo=TRUE}
set.seed(20)
x<-rnorm(100)
e<-rnorm(100,0,2)
data<-0.5+2*x+e
mean(data)
mean(remove.Outliers(data))
plot(x,data,col ="blue")
data
remove.Outliers(data)

```
## Question4
Write a function called how.many that takes 2 arguments(data and value).
The function should return a value indicating how many times the element
"value" occured in the vector data.
```{r,echo=TRUE}
how.many<-function(data,value){
  frequency.value<-data == value
  output<-sum(frequency.value)
  return(output)
}
how.many(data = c(2,3,5,3,1,6,2),value = 3)